Understanding GDP Relations to Crime in US Cities

### 2017-03-08 resource/index.Rmd
clean up

---
title: "Understanding GDP Relations to Crime in US Cities"
author: "Kai Yoshino, Isabella Spaletta, Chrisopther Ross, Marisa Nanakul"
date: "March 6, 2017"
output: html_document
---
<br>

@@

For this research project we decided to use two datasets for our analysis; one for crime based data on U.S. cities over a 5 year time period (2010-2015), and one for the GDP for metropolitan areas in the U.S. over a 5 year time period (2010-2015).

@@

You can see a sample of what the crime dataset looks like (shows all 5 years) [Here](../resource/crime-dataset.html).

@@

@@

>>>>

---
title: "Understanding GDP Relations to Crime in US Cities"
author: "Kai Yoshino, Isabella Spaletta, Chrisopther Ross, Marisa Nanakul"
date: "March 6, 2017"
output: html_document
---

@@

For this research project we decided to use two datasets for our analysis; one for [crime based data](https://ucr.fbi.gov/crime-in-the-u.s/2015/crime-in-the-u.s.-2015/tables/table-8/table_8_offenses_known_to_law_enforcement_by_state_by_city_2015.xls/view) on U.S. cities over a 5 year time period (2010-2015), and one for the [GDP for metropolitan areas](https://www.bea.gov/national/index.htm) in the U.S. over a 5 year time period (2010-2015).

@@

You can see a sample of how we formatte the crime dataset (all 5 years) [Here](../resource/crime-dataset.html).

@@

<br>

@@

<br>
<br>
<br>
